Reanalysis Step 7: Missingness Pattern Analysis

### 2025-09-01 reanalysis-7-missingness_patterns.qmd
better diagnostics for missingness

# Additional packages for this analysis
library(knitr)
library(tableone)
library(ggplot2)
library(gridExtra)

@@

# Load the original data before exclusions
original_data <- readRDS(file.path(reanalysis_data_dir, "cai_lapse_data_processed.rds"))

>>>>

# Additional packages for this analysis
library(readr)
library(knitr)
library(tableone)
library(ggplot2)
library(gridExtra)

@@

# Load the original data before exclusions
# This is the combined data file that includes all patients before any exclusions
original_data <- read_csv(reanalysis_data_file_path, show_col_types = FALSE)
